---
title: "Field Study Data Analysis"
author: "Lucas Nebert"
date: "`r date()`"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "/home/lucas/Main/Illumina/seed-microbes/dada2/16S_final")

library(ggplot2)
library(reshape2)
library(phyloseq)
library(dplyr)
library(vegan)


set.seed(100)
```


Project Aims:
1. Determine main differences between bacterial and fungal endophyte communities between corn crowns and seeds
2. Delineate likely sources for seed associated endophytes, including crown, silk, and soil
3. Find putative microbe-microbe relationships through co-occurrence patterns
4. Determine functional significance of bacterial and fungal endophytes on plant disease status


Aim 1. Determine main differences between bacterial and fungal endophyte communities between corn crowns and seeds

Subset samples to include only the "controls" i.e. those that were not treated in any way, in addition to corn silks and soil
```{r subset samples}
ps0 <- readRDS("16S.ps.Rds")
ps1 <-subset_samples(ps0, Disinfection != 1 & Inoculation != 1 | DNA_plate_number == 3)
ps1 <- prune_taxa(taxa_sums(ps1) > 0, ps1)
ps1

```


```{r make tree}
ps.genus <- tax_glom(ps1,"Genus", NArm =TRUE)
ps.class <- tax_glom(ps1,"Class", NArm =TRUE)

taxa_names(ps.genus) <- tax_table(ps.genus)[,6]
plot_tree(ps.genus, method='treeonly', ladderize="left",label.tips="taxa_names")
taxa_names(ps.class) <- tax_table(ps.class)[,3]
plot_tree(ps.class, method='treeonly', ladderize="left",label.tips="taxa_names")
```
Alpha Diversity

```{r alpha diversity}
p <- plot_richness(ps1, color = "Tissue", x = "Tissue", measures = c("Observed", "Chao1", "Shannon", "Simpson", "InvSimpson"))
p <- p + geom_boxplot(aes(fill = Tissue), alpha=0.1)
plot(p)

plot(sort(sample_sums(ps1)))

ps1 <- add_alpha_diversity(ps1)
ps1 <- add_alpha_rarefaction(ps1)

```


Ordinate the data
```{r ordinations}
ord = ordinate(ps1, method = "NMDS", distance = "bray")
plot_ordination(ps1, ord, color = "Tissue") + ggtitle("NMDS: Bray-Curtis")

ord = ordinate(ps1, method = "NMDS", distance = "unifrac")
plot_ordination(ps1, ord, color = "Tissue") + ggtitle("NMDS: UniFrac")


# remove sample 2, outlier
ps2 <- subset_samples(ps1,SampleID!="Sample2")

ord = ordinate(ps2, method = "NMDS", distance = "bray")
plot_ordination(ps2, ord, color = "Tissue") + ggtitle("NMDS: Bray-Curtis") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"))

ord = ordinate(ps2, method = "NMDS", distance = "unifrac")
plot_ordination(ps2, ord, color = "Tissue") + ggtitle("NMDS: UniFrac")

ord = ordinate(ps2, method = "PCoA", distance = "bray")
plot_ordination(ps2, ord, color = "Tissue") + ggtitle("PCoA: Bray-Curtis")

```
```{r contstrained ordination}
ps1 <- subset_samples

```

```{r shared}
taxa_names(ps1) <- paste0("RSV_",seq(1,length(taxa_names(ps1))))

ps1.pa <- transform_sample_counts(ps1,function(x)1*(x>0))

library("betapart")
shared <- data.frame(betapart.core(otu_table(ps1.pa))$shared)



library(plyr)
psm <- psmelt(ps)
sd <- sample_data(ps1)
View(sd)


df <- data.frame(sd$Tissue, sd$Sample_type)
rownames(df) <- rownames(sd)

a <- aggregate(data=sample_data(ps1),SampleID ~ Tissue)
```

ps.ds <- readRDS("16S.ps.ds.Rds")
ps.pa <- readRDS("16S.ps.pa.Rds")
ps.ra <- readRDS("16S.ps.ra.Rds")
